The Mass Distribution of Stellar-Mass Black Holes

### 2010-10-22 paper.tex
Charles' quick changes.

An important part of any Bayesian analysis is the priors placed on the
parameters of the model.  The choice of priors can bias the results of
the analysis through both the shape and the range of prior support in
parameter space.

@@

\citet{Fryer2001} suggest that the black-hole mass distribution may be
well-represented by a decaying exponential with a minimum mass:
\begin{equation}
  \label{eq:exp-def}
  p(M|\vtheta) = p(M|\{\Mmin, M_0\}) = 
  \begin{cases}
    \frac{e^{\frac{\Mmin}{M_0}}}{M_0} \exp \left[ - \frac{M}{M_0}
    \right] & \Mmin \leq M \\
    0 & \textnormal{otherwise}
  \end{cases}.
\end{equation}
We choose a prior for this model where $\Mmin$ is uniform between 0
and $40 \Msun$.  For each $\Mmin$, we choose $M_0$ uniformly within a
range ensuring that $40\Msun$ is at least two scale masses above the
cutoff: $40\Msun \geq \Mmin + 2 M_0$.  This ensures that the majority
of the mass probability lies in the range $0 \leq M \leq 40\Msun$.
The resulting prior is
\begin{equation}
  p(\vtheta) = p(\{\Mmin, M_0\}) = 
  \begin{cases}
    \frac{4}{40^2} & 0 \leq \Mmin \leq 40, \quad 0 < M_0, \quad \Mmin
    + 2 M_0 \leq 40, \\
    0 & \textnormal{otherwise}
  \end{cases}
\end{equation}

@@

\begin{figure}
  \begin{center}
    \plottwo{plots/dist-parametric-high}{plots/dist-non-parametric-high}
  \end{center}
  \caption{\label{fig:high-mass-dists} The median values of the black
    hole mass distribution, $p(M|\theta)$, at various masses implied
    by the posterior $p(\theta|d)$ for the models discussed in
    Sections \ref{sec:parametric-models} and
    \ref{sec:non-parametric-models}.  These distributions use the
    complete sample of 20 observations in Table \ref{tab:sources},
    including the higher-mass, wind-fed systems.  Error bars span the
    10\% to 90\% range.  Note that these ``distributions of
    distributions'' are not necessarily normalized, and need not be
    ``shaped'' like the underlying model distributions.  Compare to
    Figure \ref{fig:dists}, which includes only the low-mass systems
    in the analysis.  Including the higher-mass systems tends to widen
    the distribution toward the high-mass end and, in models that
    allow it, produce a second, higher-mass peak in addition to the
    one in Figure \ref{fig:dists}. }
\end{figure}

>>>>

An important part of any Bayesian analysis is the priors placed on the
parameters of the model.  The choice of priors can bias the results of
the analysis through both the shape and the range of prior support in
parameter space.  The prior should reflect the ``best guess'' for the
distribution of parameters before examining any of the data.  In the
absence of any information about the distribution of parameters, it is
best to choose a prior that is broad and uniformative to avoid biasing
the posterior as much as possible.

@@

\citet{Fryer2001} suggest that the black-hole mass distribution may be
well-represented by a decaying exponential with a minimum mass:
\fixme{Vicky, do you want to say anything more here?}
\begin{equation}
  \label{eq:exp-def}
  p(M|\vtheta) = p(M|\{\Mmin, M_0\}) = 
  \begin{cases}
    \frac{e^{\frac{\Mmin}{M_0}}}{M_0} \exp \left[ - \frac{M}{M_0}
    \right] & M \geq \Mmin \\
    0 & \textnormal{otherwise}
  \end{cases}.
\end{equation}
We choose a prior for this model where $\Mmin$ is uniform between 0
and $40 \Msun$.  For each $\Mmin$, we choose $M_0$ uniformly within a
range ensuring that $40\Msun$ is at least two scale masses above the
cutoff: $40\Msun \geq \Mmin + 2 M_0$.  This ensures that the majority
of the mass probability lies in the range $0 \leq M \leq 40\Msun$.
The resulting prior is
\begin{equation}
  p(\vtheta) = p(\{\Mmin, M_0\}) = 
  \begin{cases}
    \frac{4}{40^2} & 0 \leq \Mmin \leq 40, \quad 0 < M_0, \quad \Mmin
    + 2 M_0 \leq 40, \\
    0 & \textnormal{otherwise}
  \end{cases}
\end{equation}

@@

\begin{figure}
  \begin{center}
    \plottwo{plots/dist-parametric-high}{plots/dist-non-parametric-high-mass}
  \end{center}
  \caption{\label{fig:high-mass-dists} The median values of the black
    hole mass distribution, $p(M|\theta)$, at various masses implied
    by the posterior $p(\theta|d)$ for the models discussed in
    Sections \ref{sec:parametric-models} and
    \ref{sec:non-parametric-models}.  These distributions use the
    complete sample of 20 observations in Table \ref{tab:sources},
    including the higher-mass, wind-fed systems.  Error bars span the
    10\% to 90\% range.  Note that these ``distributions of
    distributions'' are not necessarily normalized, and need not be
    ``shaped'' like the underlying model distributions.  Compare to
    Figure \ref{fig:dists}, which includes only the low-mass systems
    in the analysis.  Including the higher-mass systems tends to widen
    the distribution toward the high-mass end and, in models that
    allow it, produce a second, higher-mass peak in addition to the
    one in Figure \ref{fig:dists}. }
\end{figure}
